---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi=200,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



# CYTAR

A package for analysing Argentina's Science and technology system (CYT)

 <!-- . -->




# Package



# How to get started (Development version)

Install the R package using the following commands on the R console:

```R
# install.packages("devtools")
devtools::install()
```

# How to use it

First add variable with your preferred configurations in `~/.Renviron`. 
 

```.Renviron
CYTAR_data_dir = "~/.R/CYTAR/"
```

```{r, library}
library(CYTAR)
library(ggplot2)
library(lgr)
```


# CYTAR analytics over people and researchs

opendata From Ministerio de Ciencia de la Nación Argentina

```{r, }
log.dir <- file.path(getEnv("data_dir"), "logs")
dir.create(log.dir, recursive = TRUE, showWarnings = FALSE)
log.file <- file.path(log.dir, "cytar.log")
lgr::get_logger("root")$add_appender(AppenderFile$new(log.file))
lgr::threshold("info", lgr::get_logger("root"))
lgr::threshold("info", lgr::get_logger("CYTARPersonal"))


personas <- CYTARPersonas$new()
self <- personas
personas$loadData()
nrow(personas$data)


personas.2018 <- CYTARPersonas2018$new()
self <- personas.2018
personas.2018$loadData()
nrow(personas.2018$data)
personas.2018$consolidate()
nrow(personas.2018$consolidated)
names(personas.2018$consolidated)



```
```{r, producciones}
library(dplyr)
library(readr)

producciones <- CYTARProducciones$new()
self <- producciones
producciones$configAll()
producciones$loadAll()
names(producciones$producciones.years)

personas.selected <- personas$data %>% filter(grepl("kornblihtt", apellido, ignore.case = TRUE))
personas.selected
producciones.personas <- producciones$getProduccionesPersonas(personas.df = personas.selected)

write_csv(producciones.personas, file = file.path(getDataDir(), "producciones_kornblihtt.csv"))

producciones.personas %>%
 group_by(persona_id, nombre, apellido, edad) %>%
 summarize( min_anio = min(anio_publica, na.rm = TRUE),
            max_anio = max(anio_publica, na.rm = TRUE),
            n        = n()
            )

```
